### 2016-12-23 README.Rmd
Remove text folder because of publisher requirements

Generated data ends up in `generated-data` and figures in `figs`. Intermediate versions of some raw data have been cached in the `generated-data` folder so that the scripts will run from a freshly cloned version of this repository. (Some of the raw data files are too large for Git.)

>>>>

Generated data ends up in `analysis/generated-data` and figures in `figs`. Intermediate versions of some raw data have been cached in the `analysis/generated-data` folder so that the scripts will run from a freshly cloned version of this repository. (Some of the raw data files are too large for Git.)
